---
title: "Farmacs by scensal"
date: '`r Sys.time()`'
output: 
  html_document: 
    toc: yes
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(knitr)
library(kableExtra)
library(survival)
library(data.table)
library(flextable)
library(officer)
library(GGally)
library(survival)
library(htmltools)
library(dplyr)
library(corrplot)
library(RColorBrewer)
library(ggpubr)
library(cluster)
library(factoextra) 
library(devtools)
library(FeatureImpCluster)
library(flexclust)
# install_github("vqv/ggbiplot")
library(ggbiplot)
knitr::opts_chunk$set(echo = FALSE)
farmacs <- readRDS('~idiap/projects/scorewater/build.data/farmacsSCOREwater2019.rds')
farmacs[is.na(farmacs)] <- -1
farmacs$ip2011 <- NULL
farmacs$cm <- NULL
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r, include=FALSE}
farmacs1 <- farmacs[farmacs$pob_IDIAP_2020 >= 0, ] # Algunes files tenien valors negatius de poblacio prevalent, em decidit treure'ls
farmacs1 <- farmacs1 %>% 
    group_by(scensal, provincia, sexe, edat) %>%
    summarize_if(is.numeric, max, na.rm = T)
farmacs1 <- farmacs1 %>% 
    group_by(provincia, scensal) %>%
    summarize_if(is.numeric, sum, na.rm = T)
farmacs$pob_IDIAP_2020 <- NULL
farmacs1$provincia <- NULL
farmacs1$nddd <- NULL
farmacs1$env <- NULL
farmacs = merge(farmacs, farmacs1)
```
# Envases per province
```{r}
autofit(flextable(farmacs[,.(N_envases=sum(env ,na.rm = T)),.(provincia)]))
```

# Envases per compound
```{r}
autofit(flextable(farmacs[,.(N_env=sum(env ,na.rm = T)),.(Compound)]))
```

## Barplot of nddd per compound
```{r, fig.width = 7, fig.height=4.5, fig.align='center'}
n_farmacs = farmacs[,.(equal=sum(nddd ,na.rm = T)),.(Compound = Compound)][]
ggplot() + 
  geom_bar(data = n_farmacs, aes(x=Compound, y=equal), stat = 'identity') +
  theme_minimal() +
  labs(x = 'Compound', y = 'nddd') +
  theme(axis.text.x = element_text(angle=90, hjust = 1))

```



```{r, include=FALSE}
# Total Number of envases of every compound * municipality
# a = farmacs[, .N, keyby = .(Compound)]
# farmaclist = a[[1]]
# fstat = function(x) factor(x, labels = farmaclist)
# farmacs[, subgrup := fstat(Compound)]
# autofit(flextable(dcast(farmacs[, sum(env ,na.rm = T), keyby = .(Compound, municipi)], Compound ~ municipi)))
```
# Tables
## 10 populations with higher prevalence (nddd/pob_IDIAP_2020)
```{r, results='asis'}
setDT(farmacs)
a = farmacs[, .N, keyby = .(Compound)]
farmaclist = a[[1]]
farmacs$pob_IDIAP_2020 <- NULL
farmacs <- farmacs %>% 
    group_by(provincia, scensal, Compound) %>%
    summarize_if(is.numeric, sum, na.rm = T)
data = merge(farmacs, farmacs1)
EV = farmaclist
data$prevalence <- data$nddd/data$pob_IDIAP_2020
for(DISEASE in EV){
    df = subset(data, Compound == DISEASE)
    scensaldata <- df[with(df,order(-prevalence)),]
    scensaldata = scensaldata[1:10,]
    scensaldata$scensal <- factor(scensaldata$scensal, levels = scensaldata$scensal)
    print(ggplot() +
            geom_bar(data = scensaldata, aes(x=scensal, y=prevalence, fill = provincia), stat = 'identity') +
            theme_minimal() +
            ggtitle(DISEASE) +
            labs(x = 'Censal code', y = ' prevalence') +
            theme(axis.text.x = element_text(angle=45, hjust = 1)))
    print(landscape(kable_styling(kable(scensaldata[1:10,]))))
    cat('----------------------------------------------------------------------------------------------------------------------------------------------------------------------------')
}
```

## 20 quantiles
```{r, results='asis'}
numberlist = c(20:1)
for(DISEASE in EV){
  table <- data.frame(Compound=character(),
                 scensal=character(), 
                 provincia=character(),
                 pob_IDIAP_2020=double(),
                 nddd = double(),
                 env = double(),
                 prevalence = double(),
                 quartile = integer(),
                 stringsAsFactors=FALSE) 
  df = subset(data, Compound == DISEASE)
  df <- df[with(df,order(-prevalence)),]
  for (number in numberlist) {
    df$quartile <- ntile(df$prevalence, 20)  
    quartils <- df[df$quartile == number, ] 
    table = rbind(table, quartils[which.max(quartils$nddd),])
  }
  table$scensal <- factor(table$scensal, levels = table$scensal)
  print(ggplot() + 
          geom_bar(data = table, aes(x=scensal, y=prevalence, fill = provincia), stat = 'identity') +
          theme_minimal() +
          ggtitle(DISEASE) +
          labs(x = 'Censal code', y = ' prevalence') +
          theme(axis.text.x = element_text(angle=45, hjust = 1)))
  table$quartile <- NULL
  print(landscape(kable_styling(kable(table))))
  cat('----------------------------------------------------------------------------------------------------------------------------------------------------------------------------')
}
```

# Barplot of nddd/month
```{r}
farmacs <- readRDS('~idiap/projects/scorewater/build.data/farmacsSCOREwater2019.rds')
farmacs[is.na(farmacs)] <- -1
farmacs$ip2011 <- NULL
farmacs$cm <- NULL
data = farmacs %>%
    group_by(month = lubridate::floor_date(date, "month"), Compound) %>%
    summarize_if(is.numeric, sum, na.rm = T)
EV = farmaclist

for(DISEASE in EV){
  df = subset(data, Compound == DISEASE)
  print(ggplot() +
    geom_bar(data = df, aes(x=month, y=nddd), stat = 'identity') +
    theme_minimal() +
    ggtitle(DISEASE) +
    labs(x = 'Month', y = ' nddd') +
    theme(axis.text.x = element_text(angle=90, hjust = 1)))
  }
```



# Cluster analysis

## Principal component analysis

* Making 3 clusters as we are interested in determining how populations with high, medium and low consumption of medicines are grouped. 
* Only the 4 features with higher importance were used

```{r}
setDT(farmacs)
a = farmacs[, .N, keyby = .(Compound)]
farmaclist = a[[1]]
farmacs$pob_IDIAP_2020 <- NULL
farmacs <- farmacs %>% 
    group_by(provincia, scensal, Compound) %>%
    summarize_if(is.numeric, sum, na.rm = T)
data = merge(farmacs, farmacs1)
data$prevalence <- data$nddd/data$pob_IDIAP_2020
data = data %>% dplyr::select(scensal, Compound, prevalence)

data = dcast(data, scensal ~ Compound, fill = 0)
z <- data[,-c(1,1)]
# means <- apply(z,2,mean)
# sds <- apply(z,2,sd)
# nor <- scale(z,center=means,scale=sds)
set.seed(10)
res <- kcca(z,k=3)
set.seed(10)
FeatureImp_res <- FeatureImpCluster(res,as.data.table(z))
a = as.data.frame(FeatureImp_res$featureImp)
# Seleccionem només els 4 farmacs més importants
z = z %>% dplyr::select(Hydrochlorothiazide, Losartan, `Acetylsalicylic acid`, Acetaminophen)
set.seed(10)
res <- kcca(z,k=3)
p = barplot(res)
```


## Cluster plot

* Even if the Optimal number of clusters is 2, we decide to keep making 3 as it matches better our interests maintaining a high Silhouette width

```{r}
distance = dist(z)
data.hclust = hclust(distance)
pca <- prcomp(z, center = TRUE,scale. = TRUE)
ggbiplot(pca)
fviz_nbclust(z, kmeans, method = "silhouette")
k2 <- kmeans(z, centers = 3, nstart = 25)
fviz_cluster(k2, data = z)
```

* 492 = censal code 0801907097
* 2615 = censal code 2501001001
* 1851 = censal code 0820005003
* 2746 = censal code 2516801001
* 2485 = censal code 1707902022
